DOpElib:\\ Differential Equations and Optimization Environment

### 2023-06-18 Examples/Documentation/introduction.tex
fixed old file header
Added Contributors Mang, Walloth

\section{License information}
Copyright (C) 2012--2017 by the DOpElib authors\\[2mm]
%
This file is part of DOpElib\\[2mm]
%
DOpElib is free software: you can redistribute it
and/or modify it under the terms of the GNU General Public
License as published by the Free Software Foundation, either
version 3 of the License, or (at your option) any later
version.\\[2mm]
%
DOpElib is distributed in the hope that it will be
useful, but WITHOUT ANY WARRANTY; without even the implied
warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR
PURPOSE.  See the GNU General Public License for more
details.\\[2mm]
%
Please refer to the file LICENSE.TXT included in this distribution
for further information on this license.

@@

We would like to express our gratitude to the former maintainer
\begin{itemize}
\item Christian Goll (Maintainer from 2009--2015)
\end{itemize}
%%% TODO: add Daniel Jodlbauer and Bernhard Endtmayer

Furthermore, there are more highly appreciated contributions
made by %(in alphabetical order)
\begin{itemize}
  \item Daniel Jodlbauer (current work on parallelization)
  \item Bernhard Endtmayer (phase-field fracture, PDE Instat Example 8 - in cooperation with T. Wick)
  \item Michael Geiger (Examples for Plasticity, and Documentation of several PDE-Examples)
  \item Masoud Ghaderi (Augmenting the Documentation)
  \item Uwe K{\"o}cher (Makefile compatibility)
  \item Francesco Ludovici (Augmenting the Documentation)
  \item Matthias Maier (CMake)
\end{itemize}

>>>>

\section{License information}
Copyright (C) 2012--2018 by the DOpElib authors\\[2mm]
%
This file is part of DOpElib\\[2mm]
%
DOpElib is free software: you can redistribute it
and/or modify it under the terms of the GNU General Public
License as published by the Free Software Foundation, either
version 3 of the License, or (at your option) any later
version.\\[2mm]
%
DOpElib is distributed in the hope that it will be
useful, but WITHOUT ANY WARRANTY; without even the implied
warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR
PURPOSE.  See the GNU General Public License for more
details.\\[2mm]
%
Please refer to the file LICENSE.TXT included in this distribution
for further information on this license.

@@

We would like to express our gratitude to the former maintainer
\begin{itemize}
\item Christian Goll (Maintainer from 2009--2015)
\end{itemize}

Furthermore, there are more highly appreciated contributions
made by %(in alphabetical order)
\begin{itemize}
  \item Seshadri Basava (Gradient robust methods for vector valued problems)
  \item Bernhard Endtmayer (phase-field fracture, PDE Instat Example 8 - in cooperation with T. Wick)
  \item Michael Geiger (Examples for Plasticity, and Documentation of several PDE-Examples)
  \item Masoud Ghaderi (Augmenting the Documentation)
  \item Daniel Jodlbauer (Current work on parallelization)
  \item Uwe K{\"o}cher (Makefile compatibility)
  \item Francesco Ludovici (Augmenting the Documentation)
  \item Matthias Maier (CMake)
  \item Katrin Mang (Rothe method for non-stationary problems,
    phase-field damage examples)
  \item Mirjam Walloth (Error estimation in non-stationary problems)
  \end{itemize}

### 2023-06-18 Examples/OPT/StatPDE/Example2/content.tex

\subsubsection{General problem description}
This example solves the following pointwise minimization problem
\begin{align*}
\min_{(q,u)\in \mathbb R^3 \times H_0^1(\Omega; \mathbb R^2)} J(q,u) &= \frac{1}{2} \sum_{i=0}^2\abs{(u-\overline u)(x_i)}^2 + \frac{\alpha}{2}\|q\|^2&&\\
\text{s.t. } (\nabla u,\nabla \phi) &= (f(q),\phi) \quad\forall\,\phi \in H^1_0(\Omega; \mathbb R^2)
\end{align*}
on the domain $\Omega = [0,1]^2$, with zero Dirichlet boundary conditions and
\begin{itemize}
\item the observation points
\begin{align*}
x_0 = (0.5, 0.5), \quad x_1 = (0.5, 0.25),\quad x_2 = (0.25, 0.25),
\end{align*}
\item the regularization parameter $\alpha = 0$, 
\item the right hand side
\begin{align*}
 f(q) &= q_0 \left(\begin{matrix}2\pi^2  \sin( \pi x) \sin(\pi y)\\0 \end{matrix}\right)\\
      &+ q_1 \left(\begin{matrix}5\pi^2  \sin( \pi x) \sin(2\pi y)\\0 \end{matrix}\right)\\
      &+ q_2 \left(\begin{matrix}0 \\8\pi^2  \sin(2\pi x) \sin(2\pi y)\end{matrix}\right)\\
\end{align*}
\item and the exact solution given by 
\begin{align*}
 \overline{q} &= \bigl(1;0.5;1\bigr)\\
 \overline{u}& = \left(\begin{matrix} \sin( \pi x)( \sin(\pi y)+0.5\sin(2\pi y))\\\sin(2\pi x) \sin(2\pi y) \end{matrix}\right).
\end{align*}
\end{itemize}
\subsubsection{Program description}
{
In contrast to the first example, the control is now a discrete quantity (for
the three observation points) where we use the \texttt{FE\underline{}Nothing}
element to assign the three controls. Here, the number of components equals
the number of controls. 
In addition, }notice that the cost functional is of mixed type (from our computational point of view), i.e. the first part is a pointfunctional whereas the regularization part requires the evaluation of a domain integral. To handle this, we need a special integrator as well as a special newtonsolver. Additionally, our \texttt{LocalFunctional} returns as his type:
\begin{verbatim}
      string
      GetType() const
      {
        return "point domain";
      }
\end{verbatim}
Indicating, we have both some point values in the functional, as well as a domain contribution, 
i.e., we calculate $\|q\| = \int_\Omega |q|\,dx$,
even though this in not necessary, since $\alpha =0$ and the euclidean 
norm of $q\in \mathbb R^3$ could be evaluated more easily using an \text{AlgebraicValue} in the functional.

>>>>

\subsubsection{General problem description}
This example solves the following pointwise minimization problem
\begin{align*}
\min_{(q,u)\in \mathbb R^3 \times H_0^1(\Omega; \mathbb R^2)} J(q,u) &= \frac{1}{2} \sum_{i=0}^2\abs{(u-\overline u)(x_i)}^2 + \frac{\alpha}{2}\|q\|^2&&\\
\text{s.t. } (\nabla u,\nabla \phi) &= (f(q),\phi) \quad\forall\,\phi \in H^1_0(\Omega; \mathbb R^2)
\end{align*}
on the domain $\Omega = [0,1]^2$, with zero Dirichlet boundary conditions and
\begin{itemize}
\item the observation points
\begin{align*}
x_0 = (0.5, 0.5), \quad x_1 = (0.5, 0.25),\quad x_2 = (0.25, 0.25),
\end{align*}
\item the regularization parameter $\alpha = 0$, 
\item the right hand side
\begin{align*}
 f(q) &= q_0 \left(\begin{matrix}2\pi^2  \sin( \pi x) \sin(\pi y)\\0 \end{matrix}\right)\\
      &+ q_1 \left(\begin{matrix}5\pi^2  \sin( \pi x) \sin(2\pi y)\\0 \end{matrix}\right)\\
      &+ q_2 \left(\begin{matrix}0 \\8\pi^2  \sin(2\pi x) \sin(2\pi y)\end{matrix}\right)\\
\end{align*}
\item and the exact solution given by 
\begin{align*}
 \overline{q} &= \bigl(1;0.5;1\bigr)\\
 \overline{u}& = \left(\begin{matrix} \sin( \pi x)( \sin(\pi y)+0.5\sin(2\pi y))\\\sin(2\pi x) \sin(2\pi y) \end{matrix}\right).
\end{align*}
\end{itemize}
\subsubsection{Program description}
{
In contrast to the first example, the control is now a discrete quantity (for
the three observation points) where we use the \texttt{FE\underline{}Nothing}
element to assign the three controls. Here, the number of components equals
the number of controls. 
In addition, }notice that the cost functional is of mixed type (from
our computational point of view), i.e. the first part is a
point-functional whereas the regularization part requires the
evaluation of a domain integral. To handle this, we need a special
integrator as well as a special Newton-solver. Additionally, our \texttt{LocalFunctional} returns as his type:
\begin{verbatim}
      string
      GetType() const
      {
        return "point domain";
      }
\end{verbatim}
Indicating, we have both some point values in the functional, as well as a domain contribution, 
i.e., we calculate $\|q\| = \int_\Omega |q|\,dx$,
even though this in not necessary, since $\alpha =0$ and the euclidean 
norm of $q\in \mathbb R^3$ could be evaluated more easily using an \text{AlgebraicValue} in the functional.

### 2023-06-18 Examples/OPT/StatPDE/Example6/content.tex

In this example, we introduce the handling of \textit{local} constraints
whereas the mixture of local and \textit{global} constraints will be discussed
in the Example \ref{OPT_Stat_MBB-Beam}. 
%
First, we implement the upper and lower control bounds in 
\texttt{localconstraints.h}, i.e,
\[
q_{\min} \leq q \leq q_{\max}.
\]
with $q_{\min} = -500$ and $q_{\max} = 500$.
The constraints are `local', by which we mean the constraints are imposed 
on the nodal values of the control vector. Thus, in the constraint 
description \texttt{localconstraints.h},
these vectors are manipulated directly without additional integration. We 
note that the constraints need to be written such, that a feasible control
generates non positive entried, i.e., we 
calculate the vector
\[
 \mathcal C(q) = \begin{pmatrix}
   q_{\min} - q\\q-q_{\max}
 \end{pmatrix}.
 \]
%
Second, the \texttt{lcc} vector is used to describe the amount of unknowns that 
need to be reserved to store the constraints, and, eventually, corresponding 
Lagrange multipliers. 
Further information can be found in \texttt{basic/constraints.h}. 
In our example, we have only one block in the control (The control is stored in 
a \texttt{deal.II::BlockVector}). Hence, the \texttt{lcc} vector has a length of 
one. 
The only entry \texttt{lcc[0]} is a vector of size two (in the case of more than one 
control block, each block would be given a size of $2$). 
Each of the two entries has a specific meaning. 
The first entry \texttt{lcc[0][\textcolor{blue}{0}] = 1} tells 
you how many local entries in the present block are locally constrained, here 
it is one local entry. ({\em Note that this entry will typically be one. 
it is not one  would be if we have constraints of the type $q_{i} + q_{i+1} \le 1$ for each 
even $i$, or similar combinations of multiple entries in the control vector.})

The second entry \texttt{lcc[0][\textcolor{blue}{1}] = 2}, determines the number of 
constraints on this local entry. Here, we impose 
a lower and an upper bound, i.e., we give 2 constraints.
This information tells the SpaceTimeHandler, that the vector 
$\mathcal C(q)$ needs exactely twice the amount of unknowns as the vector $q$.
In general, the space needed for $\mathcal C(q)$ is given as 
\[
\frac{\text{\texttt{lcc[0][1]}}}{\text{\texttt{lcc[0][0]}}}
\]
times the unknowns for the control.

>>>>

In this example, we introduce the handling of \textit{local} constraints
whereas the mixture of local and \textit{global} constraints will be discussed
in the Example \ref{OPT_Stat_MBB-Beam}. 
%
First, we implement the upper and lower control bounds in 
\texttt{localconstraints.h}, i.e,
\[
q_{\min} \leq q \leq q_{\max}.
\]
with $q_{\min} = -500$ and $q_{\max} = 500$.
The constraints are `local', by which we mean the constraints are imposed 
on the nodal values of the control vector. Thus, in the constraint 
description \texttt{localconstraints.h},
these vectors are manipulated directly without additional integration. We 
note that the constraints need to be written such, that a feasible control
generates non positive entries, i.e., we 
calculate the vector
\[
 \mathcal C(q) = \begin{pmatrix}
   q_{\min} - q\\q-q_{\max}
 \end{pmatrix}.
 \]
%
Second, the \texttt{lcc} vector is used to describe the amount of unknowns that 
need to be reserved to store the constraints, and, eventually, corresponding 
Lagrange multipliers. 
Further information can be found in \texttt{basic/constraints.h}. 
In our example, we have only one block in the control (The control is stored in 
a \texttt{deal.II::BlockVector}). Hence, the \texttt{lcc} vector has a length of 
one. 
The only entry \texttt{lcc[0]} is a vector of size two (in the case of more than one 
control block, each block would be given a size of $2$). 
Each of the two entries has a specific meaning. 
The first entry \texttt{lcc[0][\textcolor{blue}{0}] = 1} tells 
you how many local entries in the present block are locally constrained, here 
it is one local entry. ({\em Note that this entry will typically be one. 
it is not one  would be if we have constraints of the type $q_{i} + q_{i+1} \le 1$ for each 
even $i$, or similar combinations of multiple entries in the control vector.})

The second entry \texttt{lcc[0][\textcolor{blue}{1}] = 2}, determines the number of 
constraints on this local entry. Here, we impose 
a lower and an upper bound, i.e., we give 2 constraints.
This information tells the SpaceTimeHandler, that the vector 
$\mathcal C(q)$ needs exactly twice the amount of unknowns as the vector $q$.
In general, the space needed for $\mathcal C(q)$ is given as 
\[
\frac{\text{\texttt{lcc[0][1]}}}{\text{\texttt{lcc[0][0]}}}
\]
times the unknowns for the control.

### 2023-06-18 Examples/OPT/StatPDE/Example7/content.tex

\subsubsection{Program description}
In addition to the previous Example \ref{OPT_Stat_Box_controlconstraints_SNOPT}, 
we consider now in addition one global constraint. To calculate the correct 
storrage needed we use the 
second argument of \texttt{constraints(lcc, 1)}, which is now one.

We use 
\texttt{localconstraints.h} and \texttt{localconstraintaccessor.h} to impose 
all constraints. First, we have again one control block with a lower and 
an upper bound, 
\[
\rho_{min} \leq q \leq \rho_{max}
\]
with $\rho_{min} = 10^{-4}$ and $\rho_{max} = 1$ ($\rho$ denotes the density
of the material). These are implemented in \texttt{localconstraintaccessor.h}.
The global constraint is the maximum volume of the material,
which should remain constant with the value $V_{\max} = 0.5$, i.e.,
\[
 \int_\Omega q - V_{\max} \,dx \le 0.
\]
Its implementation is 
provided in \texttt{localconstraints.h} where the global constraint is handled as 
a functional, which again is normalized to be nonpositive if the control is feasible.

>>>>

\subsubsection{Program description}
In addition to the previous Example \ref{OPT_Stat_Box_controlconstraints_SNOPT}, 
we consider now in addition one global constraint. To calculate the correct 
storage needed we use the 
second argument of \texttt{constraints(lcc, 1)}, which is now one.

We use 
\texttt{localconstraints.h} and \texttt{localconstraintaccessor.h} to impose 
all constraints. First, we have again one control block with a lower and 
an upper bound, 
\[
\rho_{min} \leq q \leq \rho_{max}
\]
with $\rho_{min} = 10^{-4}$ and $\rho_{max} = 1$ ($\rho$ denotes the density
of the material). These are implemented in \texttt{localconstraintaccessor.h}.
The global constraint is the maximum volume of the material,
which should remain constant with the value $V_{\max} = 0.5$, i.e.,
\[
 \int_\Omega q - V_{\max} \,dx \le 0.
\]
Its implementation is 
provided in \texttt{localconstraints.h} where the global constraint is handled as 
a functional, which again is normalized to be non-positive if the control is feasible.

### 2023-06-18 Examples/PDE/InstatPDE/Example5/content.tex
add examples to parallel-dev

This example differs only slightly from the previous one. Again, we consider the heat equation, this time with an additional nonlinear term
\begin{equation*}
\partial_t u(t,x,y) - \Delta u(t,x,y) + u(t,x,y)^2 = f(t,x,y),
\end{equation*}
but now in two space dimensions and with known solution 
\begin{equation*}
u(t,x,y) = e^{t-t^2} \sin(x) \sin(y).
\end{equation*}
The computational domain is $\Omega \times I = [0,\pi]^2 \times [0,1]$. From the known solution, we can compute the appropriate data 
\begin{align*}
f(t,x,y) &= (3-2t)e^{t-t^2} \sin(x) \sin(y) + e^{(t-t^2)^2} \sin^2(x) \sin^2(y),\\
u_0(x,y) &= \sin(x) \sin(y).
\end{align*}
Furthermore, we have to prescribe homogeneous Dirichlet boundary conditions.

@@

The new feature of this example is the nonhomogeneous righthand side. In examples \ref{PDE_Stat_Laplace_2D} and \ref{PDE_Stat_Laplace_3D}, we regarded stationary problems with nonhomogeneous righthand sides, but up to now, we never involved the time variable into the nonhomogeneity. To do this, \texttt{DOpElib} yields a \texttt{SetTime()} function which has to be applied in the \textit{localpde.h} file as well as at the place where the \texttt{RightHandSideFunction} class is declared (here the \textit{myfunctions.h} file.

>>>>

This example differs only slightly from the previous one. Again, we consider the heat equation, this time with an additional nonlinear term
\begin{equation*}
\partial_t u(t,x,y) - \Delta u(t,x,y) + u(t,x,y)^2 = f(t,x,y),
\end{equation*}
but now in two space dimensions and with known solution 
\begin{equation*}
u(t,x,y) = e^{t-t^2} \sin(x) \sin(y).
\end{equation*}
The computational domain is $I\times\Omega = [0,1]\times [0,\pi]^2$. From the known solution, we can compute the appropriate data 
\begin{align*}
f(t,x,y) &= (3-2t)e^{t-t^2} \sin(x) \sin(y) + e^{(t-t^2)^2} \sin^2(x) \sin^2(y),\\
u_0(x,y) &= \sin(x) \sin(y).
\end{align*}
Furthermore, we have to prescribe homogeneous Dirichlet boundary conditions.

@@

The new feature of this example is the non-homogeneous right hand side. In examples \ref{PDE_Stat_Laplace_2D} and \ref{PDE_Stat_Laplace_3D}, we regarded stationary problems with non-homogeneous right hand sides, but up to now, we never involved the time variable into the non-homogeneity. To do this, \texttt{DOpElib} yields a \texttt{SetTime()} function which has to be applied in the \textit{localpde.h} file as well as at the place where the \texttt{RightHandSideFunction} class is declared (here the \textit{myfunctions.h} file.

### 2023-06-18 Examples/PDE/StatPDE/Example1/content.tex

As code verification, we evaluate two different types of functionals. 
First a point functional measuring the $x$-velocity and 
a flux functional 
\[
\int_{\Gamma_{out}} v\cdot n \, ds,
\]
on the outflow boundary. Both a described in the 
\texttt{functionals.h} file as described below.

@@

\vspace{0.2cm}
\index{functional evaluation}
Here, we declare all quantities of interest (functionals), e.g. point values, drag, lift, mean values of certain quantities over a subdomain etc. \\
Each of these functionals is declared as a class of its own, but in \texttt{DOpElib} all classes are derived from a so-called \texttt{FunctionalInterface} class.\\
As already mentioned previsously, in the current example we declare functionals for point values of the velocity and for the flux at the outflow boundary of the channel.\index{functional!point value} \index{functional!boundary flux}\\

>>>>

As code verification, we evaluate two different types of functionals. 
First a point functional measuring the $x$-velocity and 
a flux functional 
\[
\int_{\Gamma_{out}} v\cdot n \, \mathrm{d}s,
\]
on the outflow boundary. Both a described in the 
\texttt{functionals.h} file as described below.

@@

\vspace{0.2cm}
\index{functional evaluation}
Here, we declare all quantities of interest (functionals), e.g. point values, drag, lift, mean values of certain quantities over a subdomain etc. \\
Each of these functionals is declared as a class of its own, but in \texttt{DOpElib} all classes are derived from a so-called \texttt{FunctionalInterface} class.\\
As already mentioned previously, in the current example we declare functionals for point values of the velocity and for the flux at the outflow boundary of the channel.\index{functional!point value} \index{functional!boundary flux}\\

### 2023-06-18 Examples/PDE/StatPDE/Example13/content.tex

Finally, the integration will utilize a special function to be declared in the \texttt{LocalPDE}, 
hence all objects must use the \texttt{LocalPDE}
and not the \texttt{PDEInterface}.
To make sure that this is the case, the \texttt{PDEProblemContainer} needs to be initialized with the following arguments
\begin{verbatim}
typedef PDEProblemContainer<LocalPDE<CDC, FDC, DOFHANDLER, VECTOR, DIM>,
    SimpleDirichletData<VECTOR, DIM>, SPARSITYPATTERN, VECTOR, DIM> OP;
\end{verbatim}

>>>>

Finally, the integration will utilize a special function to be declared in the \texttt{LocalPDE}, 
hence all objects must use the \texttt{LocalPDE}
and not the \texttt{PDEInterface}.
To make sure that this is the case, the \texttt{PDEProblemContainer} needs to be initialized with the following arguments
\begin{verbatim}
typedef PDEProblemContainer<LocalPDE<EDC, FDC, DOFHANDLER, VECTOR, DIM>,
    SimpleDirichletData<VECTOR, DIM>, SPARSITYPATTERN, VECTOR, DIM> OP;
\end{verbatim}

### 2023-06-18 Examples/PDE/StatPDE/Example17/content.tex

 For the discretization we search $(\textbf{u}_h,p_h) \in V_h \times Q_h$,
 here given by continuous $Q_2$ finite elements for $V_h$ and discontinuous
 $Q_1$ finite elements for $Q_h$.
 The gradient robust discretization of \eqref{eq:strong_form} is given as
  \begin{align}
   2\mu \int\limits_\Omega \varepsilon(\textbf{u}_h) : \varepsilon(\textbf{v}_h) \; \mathrm{d} x + 
   \int\limits_\Omega p_h \nabla \cdot \textbf{v}_h \; \mathrm{d} x & = \int\limits_\Omega \textbf{f} \cdot  \bm{\pi}^{\rm{div}} \textbf{v}_h \; \mathrm{d} x  \label{eq:modified_weak_form} , \\
   \int\limits_\Omega q_h \nabla \cdot \textbf{u}_h \; \mathrm{d} x  - \dfrac{1}{\lambda}\int\limits_\Omega p_hq_h \; \mathrm{d} x  & = 0  \label{eq:nearly_incompress_modified}
 \end{align}
 for all $\textbf{v}_h \in V_h$, $q_h \in Q_h$
 where, $\bm{\pi}^{\rm{div}} \colon V_h\rightarrow X_h \subset H^{\rm{div}}$
 is a suitable interpolation operator satisfying
 \[
 (q_h, \nabla \cdot \textbf{v}_h) = (q_h \nabla \cdot \bm{\pi}^{\rm{div}}\textbf{v}_h) 
 \]
 for all $q_h \in Q_h$ and $\textbf{v}_h \in V_h$. For the choice of $V_h,Q_h$ made here a
 suitable choice for this space $X_h$ is the space of Raviart-Thomas finite elements
 with the canonical interpolation.

>>>>

 For the discretization we search $(\textbf{u}_h,p_h) \in V_h \times Q_h$,
 here given by continuous $Q_2$ finite elements for $V_h$ and discontinuous
 $P_1$ finite elements for $Q_h$.
 The gradient robust discretization of \eqref{eq:strong_form} is given as
  \begin{align}
   2\mu \int\limits_\Omega \varepsilon(\textbf{u}_h) : \varepsilon(\textbf{v}_h) \; \mathrm{d} x + 
   \int\limits_\Omega p_h \nabla \cdot \textbf{v}_h \; \mathrm{d} x & = \int\limits_\Omega \textbf{f} \cdot  \bm{\pi}^{\rm{div}} \textbf{v}_h \; \mathrm{d} x  \label{eq:modified_weak_form} , \\
   \int\limits_\Omega q_h \nabla \cdot \textbf{u}_h \; \mathrm{d} x  - \dfrac{1}{\lambda}\int\limits_\Omega p_hq_h \; \mathrm{d} x  & = 0  \label{eq:nearly_incompress_modified}
 \end{align}
 for all $\textbf{v}_h \in V_h$, $q_h \in Q_h$
 where, $\bm{\pi}^{\rm{div}} \colon V_h\rightarrow X_h \subset H^{\rm{div}}$
 is a suitable interpolation operator satisfying
 \[
 (q_h, \nabla \cdot \textbf{v}_h) = (q_h \nabla \cdot \bm{\pi}^{\rm{div}}\textbf{v}_h) 
 \]
 for all $q_h \in Q_h$ and $\textbf{v}_h \in V_h$. For the choice of $V_h,Q_h$ made here a
 suitable choice for this space $X_h$ is the space of Brezzi-Douglas-Marini $\mathcal{BDM}_2$ elements
 with the canonical interpolation.

### 2023-06-18 Examples/PDE/StatPDE/Example5/content.tex

As we approximate the so called 'weights' $z-\phi_h$ in the error representation by a patchwise higher order interpolation of $z_h$ (the computed dual solution), we have to enforce patch-wise refinement of the grid by giving the flag 
\begin{verbatim}
Triangulation<2>::MeshSmoothing::patch_level_1
\end{verbatim}
to the triangulation.

@@

To build this, we need the following:
\begin{itemize}
\item {\verb DOFH_higher_order }: With some higher order Finite Elements and the already defined triangulation, we build this \texttt{SpaceTimeHandler}. This is needed because  we want to use the patch-wise higher order interpolation of the weights.
\item {\verb idc_high }: A \texttt{IntegratorDataContainer} in which we put some (face)quadrature formulas for the evaluation of the error Identity.
\item A string which indicates how we want to store the weight-vectors (here: { \verb "fullmem" }).
\item \texttt{pr}: The \texttt{ParameterReader} which we have already defined.
\item A enum of type \texttt{EETerms} that tells the container, which error terms we want to compute (primal error indicators vs. dual error indicators, see \cite{BR03}).  
\end{itemize}
The last preparation step is now to initialize the \texttt{DWRDataContainer} with the problem in use:
\begin{verbatim}
  solver.InitializeHigherOrderDWRC(dwrc);
\end{verbatim}

>>>>

As we approximate the so called 'weights' $z-\phi_h$ in the error representation by a patch-wise higher order interpolation of $z_h$ (the computed dual solution), we have to enforce patch-wise refinement of the grid by giving the flag 
\begin{verbatim}
Triangulation<2>::MeshSmoothing::patch_level_1
\end{verbatim}
to the triangulation.

@@

To build this, we need the following:
\begin{itemize}
\item {\verb DOFH_higher_order }: With some higher order Finite Elements and the already defined triangulation, we build this \texttt{SpaceTimeHandler}. This is needed because  we want to use the patch-wise higher order interpolation of the weights.
\item {\verb idc_high }: A \texttt{IntegratorDataContainer} in which we put some (face)quadrature formulas for the evaluation of the error Identity.
\item A string which indicates how we want to store the weight-vectors (here: { \verb "fullmem" }).
\item \texttt{pr}: The \texttt{ParameterReader} which we have already defined.
\item An enum of type \texttt{EETerms} that tells the container, which error terms we want to compute (primal error indicators vs. dual error indicators, see \cite{BR03}).  
\end{itemize}
The last preparation step is now to initialize the \texttt{DWRDataContainer} with the problem in use:
\begin{verbatim}
  solver.InitializeHigherOrderDWRC(dwrc);
\end{verbatim}
